Appendix to "New Metrics for Assessing Projection Pursuit Indexes, and Guiding Optimisation Choices

### 2025-03-02 jso.qmd
trimmed down table 1

```{r}
#| label: tbl-smoothness-squintability
#| tbl-cap: Parameters estimated from the Gaussian process (outputscale $\eta$, lengthscale $\ell$, smoothness $\nu$, and nugget $\sigma$) and scaled logistic function ($\theta_1$ to $\theta_4$ and $\varsigma$) for the pipe-finding and sine-wave finding problems.  The columns $\nu$ and $\varsigma$ represent the smoothness and squintability measures respectively.
dt <- tibble(shape = c(rep("pipe", 5), rep("sine", 17)), smoothness) |>
  left_join(squintability) |> 
  rename(d = n, smooth = smoothness) |> 
  mutate(index = ifelse(index == "dcor2d_2", "dcor", index),
         index = ifelse(index == "loess2d", "loess", index),
         index = ifelse(index == "splines2d", "splines", index),
         variance = sqrt(variance)) 
dt |> 
  knitr::kable(
    digits = 2, format = "latex", 
    col.names = c(
      "shape", "index", "d",
      "$\\eta$", "$\\ell$", "$\\nu$", "$\\sigma$",
      "$\\theta_1$", "$\\theta_2$", "$\\theta_3$", "$\\theta_4$", "$\\varsigma$"), linesep = "",
    booktabs = TRUE, escape = FALSE, row.names = FALSE, align = "|llr|rrrr|rrrrr") |> 
  #column_spec(1, border_left = TRUE) |> 
  #column_spec(c(4, 8, 13), border_right = TRUE) |> 
  kable_styling(font_size = 10) 
```

>>>>

```{r}
#| label: tbl-smoothness-squintability
#| tbl-cap: Parameters estimated from the Gaussian process (outputscale $\eta$, lengthscale $\ell$, smoothness $\nu$, and nugget $\sigma$) and scaled logistic function ($\theta_1$ to $\theta_4$ and $\varsigma$) for the pipe-finding and sine-wave finding problems.  The columns $\nu$ and $\varsigma$ represent the smoothness and squintability measures respectively.
dt <- tibble(shape = c(rep("pipe", 5), rep("sine", 17)), smoothness) |>
  left_join(squintability) |> 
  rename(d = n, smooth = smoothness) |> 
  mutate(index = ifelse(index == "dcor2d_2", "dcor", index),
         index = ifelse(index == "loess2d", "loess", index),
         index = ifelse(index == "splines2d", "splines", index),
         variance = sqrt(variance)) 
dt |> 
  filter(shape == "sine", index %in% c("TIC", "splines", "skinny")) |>
  select(shape, index, d, smooth, squint) |>
  arrange(desc(squint)) |>
  knitr::kable(
    digits = 4, format = "latex", 
    col.names = c(
      "shape", "index", "d",
      #"$\\eta$", "$\\ell$", 
      "$\\nu$", #"$\\sigma$",
      #"$\\theta_1$", "$\\theta_2$", "$\\theta_3$", "$\\theta_4$", 
      "$\\varsigma$"), linesep = "",
    booktabs = TRUE, escape = FALSE, row.names = FALSE, align = "|llr|rr") #align = "|llr|rrrr|rrrrr") |> 
  #column_spec(1, border_left = TRUE) |> 
  #column_spec(c(4, 8, 13), border_right = TRUE) |> 
  #kable_styling(font_size = 10) 
```

### 2025-03-02 jso.tex
trimmed down table 1

\begin{tcolorbox}[enhanced jigsaw, colback=white, colbacktitle=quarto-callout-note-color!10!white, opacitybacktitle=0.6, opacityback=0, bottomtitle=1mm, leftrule=.75mm, breakable, arc=.35mm, colframe=quarto-callout-note-color-frame, title={Algorithm: Jellyfish Optimizer Pseudo Code}, coltitle=black, titlerule=0mm, toptitle=1mm, rightrule=.15mm, left=2mm, toprule=.15mm, bottomrule=.15mm]

@@

\centering\begingroup\fontsize{10}{12}\selectfont

\begin{tabular}{|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr|llr|rrrr|rrrrr}
\toprule
shape & index & d & $\eta$ & $\ell$ & $\nu$ & $\sigma$ & $\theta_1$ & $\theta_2$ & $\theta_3$ & $\theta_4$ & $\varsigma$\\
\midrule
pipe & holes & 4 & 0.03 & 0.36 & 2.99 & 0.00 & 1.00 & 0.78 & 4.50 & 0.03 & 0.31\\
pipe & holes & 6 & 0.03 & 0.38 & 3.09 & 0.00 & 1.02 & 0.86 & 3.37 & 0.02 & 0.41\\
pipe & holes & 8 & 0.02 & 0.33 & 2.90 & 0.00 & 1.01 & 0.87 & 3.26 & 0.03 & 0.41\\
pipe & holes & 10 & 0.02 & 0.34 & 2.88 & 0.00 & 1.02 & 0.88 & 3.15 & 0.02 & 0.43\\
pipe & holes & 12 & 0.02 & 0.43 & 2.72 & 0.00 & 1.01 & 0.88 & 3.34 & 0.00 & 0.41\\
sine & MIC & 4 & 0.14 & 0.27 & 3.56 & 0.00 & 0.94 & 0.15 & 1.14 & -0.04 & 0.39\\
sine & MIC & 6 & 0.06 & 0.31 & 3.08 & 0.00 & 0.89 & 0.57 & 1.62 & -0.03 & 0.39\\
sine & MIC & 8 & 0.03 & 0.32 & 2.75 & 0.00 & 0.93 & 0.33 & 1.31 & -0.04 & 0.38\\
sine & TIC & 4 & 0.40 & 0.27 & 3.49 & 0.00 & 0.97 & 0.46 & 1.55 & -0.04 & 0.38\\
sine & TIC & 6 & 0.16 & 0.31 & 3.08 & 0.00 & 0.95 & 0.54 & 1.72 & -0.03 & 0.37\\
sine & TIC & 8 & 0.07 & 0.30 & 2.72 & 0.00 & 0.95 & 0.56 & 1.72 & -0.03 & 0.38\\
sine & dcor & 4 & 0.22 & 0.30 & 3.63 & 0.00 & 0.96 & 1.07 & 2.67 & -0.03 & 0.56\\
sine & dcor & 6 & 0.08 & 0.29 & 3.13 & 0.00 & 0.95 & 1.04 & 2.74 & -0.03 & 0.53\\
sine & loess & 4 & 0.34 & 0.50 & 2.90 & 0.00 & 1.02 & 1.10 & 2.50 & 0.05 & 0.57\\
sine & loess & 6 & 0.24 & 0.46 & 3.56 & 0.00 & 1.02 & 1.04 & 2.65 & 0.07 & 0.53\\
sine & loess & 8 & 0.19 & 0.46 & 3.36 & 0.00 & 1.02 & 1.04 & 2.62 & 0.08 & 0.53\\
sine & skinny & 6 & 0.05 & 0.19 & 2.24 & 0.01 & 0.83 & 0.00 & 2.98 & 0.05 & 0.10\\
sine & splines & 4 & 0.24 & 0.32 & 3.55 & 0.00 & 1.01 & 1.09 & 2.65 & -0.03 & 0.57\\
sine & splines & 6 & 0.10 & 0.32 & 3.11 & 0.00 & 1.01 & 1.05 & 2.73 & -0.02 & 0.54\\
sine & splines & 8 & 0.05 & 0.29 & 2.74 & 0.00 & 1.02 & 1.06 & 2.68 & -0.02 & 0.54\\
sine & stringy2 & 4 & 0.02 & 0.30 & 2.76 & 1.01 & 0.64 & 0.05 & 7.89 & 0.05 & 0.00\\
sine & stringy2 & 6 & 0.02 & 0.07 & 1.51 & 0.05 & 0.65 & 0.05 & 7.78 & 0.06 & 0.00\\
\bottomrule
\end{tabular}
\endgroup{}

>>>>

\begin{tcolorbox}[enhanced jigsaw, opacitybacktitle=0.6, bottomrule=.15mm, toprule=.15mm, colback=white, colframe=quarto-callout-note-color-frame, leftrule=.75mm, coltitle=black, breakable, left=2mm, opacityback=0, bottomtitle=1mm, titlerule=0mm, colbacktitle=quarto-callout-note-color!10!white, arc=.35mm, toptitle=1mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, rightrule=.15mm]

@@

\begin{tabular}{|llr|rr|llr|rr|llr|rr|llr|rr|llr|rr}
\toprule
shape & index & d & $\nu$ & $\varsigma$\\
\midrule
sine & splines & 4 & 3.5489 & 0.5723\\
sine & splines & 6 & 3.1149 & 0.5415\\
sine & splines & 8 & 2.7400 & 0.5394\\
sine & TIC & 4 & 3.4854 & 0.3839\\
sine & TIC & 8 & 2.7223 & 0.3785\\
sine & TIC & 6 & 3.0807 & 0.3747\\
sine & skinny & 6 & 2.2352 & 0.0973\\
\bottomrule
\end{tabular}

### 2025-03-02 supplementary/index-def.qmd
trimmed down table 1

>>>>

# Gaussian process estimates for all PP indexes and data sets

```{r}
#| label: tbl-smoothness-squintability
#| tbl-cap: Parameters estimated from the Gaussian process (outputscale $\eta$, lengthscale $\ell$, smoothness $\nu$, and nugget $\sigma$) and scaled logistic function ($\theta_1$ to $\theta_4$ and $\varsigma$) for the pipe-finding and sine-wave finding problems.  The columns $\nu$ and $\varsigma$ represent the smoothness and squintability measures respectively.
dt <- tibble(shape = c(rep("pipe", 5), rep("sine", 17)), smoothness) |>
  left_join(squintability) |> 
  rename(d = n, smooth = smoothness) |> 
  mutate(index = ifelse(index == "dcor2d_2", "dcor", index),
         index = ifelse(index == "loess2d", "loess", index),
         index = ifelse(index == "splines2d", "splines", index),
         variance = sqrt(variance)) 
dt |> 
  knitr::kable(
    digits = 2, format = "latex", 
    col.names = c(
      "shape", "index", "d",
      "$\\eta$", "$\\ell$", "$\\nu$", "$\\sigma$",
      "$\\theta_1$", "$\\theta_2$", "$\\theta_3$", "$\\theta_4$", "$\\varsigma$"), linesep = "",
    booktabs = TRUE, escape = FALSE, row.names = FALSE, align = "|llr|rrrr|rrrrr") |> 
  #column_spec(1, border_left = TRUE) |> 
  #column_spec(c(4, 8, 13), border_right = TRUE) |> 
  kable_styling(font_size = 10) 
```
